Insert the article title here

### 2018-06-25 writeup/manuscript.tex
A few edits

\begin{fmtext}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%[TRIED A DIFFERENT, FEEL FREE TO CHANGE BACK
Anybody who has ever conducted a visual search experiment will be aware of the large differences from one participant to the next. These differences could be emerge from several different sources of variation: tiredness\cite{mackworth1948}, information-processing ability, speed-accuracy trade-off, motivation, visual impairments, and search strategies\cite{boot2006}. Although their existence has previously been noted \cite{mackworth1948}, a rigorous examination of individual differences in visual search has been largely ignored and questions about their importance and stability remain relatively under explored.

[MIGHT BE GOOD TO EXPLAIN HERE THAT THE EMPHASIS IS ON STRATEGY?] In the current study, we focus on one source of individual differences in visual search: strategy. By visual search strategies, we refer to a collection of behaviours that all observers can freely choose to engage in when they search a display, which is distinct from intrinsically unchanging characteristics such as information-processing ability [NOT REALLY SURE HOW BEST TO SAY THAT, JUST THOUGHT IT MIGHT BE GOOD TO HAVE SOME OF DEFINITION OF VS STRATS??]. Recent studies have shown substantial variation in search strategies across individuals.

A striking example of the effect of strategy is given by \cite{boot2006, boot2009}. They found differences in visual search performance could be explained by whether observers used a [active?] scanning strategy, or simply fixated the centre of the stimulus and used covert attention to search peripheral vision.

@@

% Memory stuff might be too left field for intro?
In the related field of memory, individual differences have received more attention, for example \cite{sobel2007}.

@@

The results for the ACVS were consistent with our previous findings \cite{irons-leber2016,irons-leber2018} (see Figure 3?). Figure 3 (? AC_OptCh_x_AllSw) shows that there were wide individual differences in both percent option (range $33.62\%$ – $97.50\%$, $M = 56.99$, $SD = 14.75$) and switch rate (range = $0\% - 56.68\%$, $M = 28.46$, $SD = 13.54$). Although we did not assess it here, good test-retest reliability has been found previously for both percent optimal ($r = .83$) and switch rate ($r = .77$) \cite{irons-leber,2018}.

@@

>>>>

\begin{fmtext}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Anybody who has ever conducted a visual search experiment will be aware of the large differences from one participant to the next. These differences could be emerge from several different sources of variation: tiredness\cite{mackworth1948}, information-processing ability, speed-accuracy trade-off, motivation, visual impairments, and search strategies\cite{boot2006}. Although their existence has previously been noted \cite{mackworth1948}, a rigorous examination of individual differences in visual search has been largely ignored and questions about their importance and stability remain relatively under explored.

In the current study, we focus on one source of individual differences in visual search: strategy. By visual search strategies, we refer to a collection of behaviours that all observers can freely choose to engage in when they search a display, which is distinct from intrinsically unchanging characteristics such as information-processing ability and motivation. Perhaps surprisingly, previous literature has shown that both ideal oberver \cite{najemnik-geisler2008} and stochastic \cite{clarke2016} models can explain the number of fixations required by an average observer to locate a target in noise. These apparent contradictory results could potentially expained by large individual differences.

A striking example of the effect of strategy is given by \cite{boot2006, boot2009}. They carried out a dynamic dot detection task 
found differences in visual search performance could be explained by whether observers used a [active?] scanning strategy, or simply fixated the centre of the stimulus and used covert attention to search peripheral vision.

@@

@@

The results for the ACVS were consistent with our previous findings \cite{irons-leber2016,irons-leber2018} (see Figure 3?). %Figure 3 (? AC_OptCh_x_AllSw) shows that there were wide individual differences in both percent option (range $33.62\%$ – $97.50\%$, $M = 56.99$, $SD = 14.75$) and switch rate (range = $0\% - 56.68\%$, $M = 28.46$, $SD = 13.54$). Although we did not assess it here, good test-retest reliability has been found previously for both percent optimal ($r = .83$) and switch rate ($r = .77$) \cite{irons-leber,2018}.

@@

% Memory stuff might be too left field for intro?
% agree, let's try and mention it in the discussion though. 
In the related field of memory, individual differences have received more attention, for example \cite{sobel2007}.
